% Page size 
\usepackage{geometry}
\geometry{
  a4paper, left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm
  %, showframe
}

% Links
\usepackage[]{hyperref}
\hypersetup{colorlinks=true,}
\usepackage{tabularx}
\usepackage{multirow}

% Fonts
\usepackage{fontspec}
\setmainfont{Open Sans}

% Add packages
\usepackage{awesomebox}

% Define colors
\definecolor{blueEC}{HTML}{004494}

\usepackage{sectsty}
\sectionfont{\color{blueEC}}  % sets colour of chapters
\subsectionfont{\color{blueEC!80}}  % sets colour of chapters
\subsubsectionfont{\color{blueEC!60}}  % sets colour of chapters

% Lists
\usepackage{enumitem}
\usepackage{tikz}

% Define a custom circle label
\newcommand*\circled[1]{%
  \tikz[baseline=(char.base)]{
    \node[shape=circle,draw=blueEC,fill=blueEC, text=white, inner sep=2pt] (char) {#1};
  }%
}

% Customize the enumerate environment
\setlist[enumerate]{
  label={\protect\circled{\arabic*}},
  leftmargin=*,
}



% Create highlight boxes
\usepackage[most]{tcolorbox}
\usepackage{enumitem}

% Custom key points textbox
% https://tex.stackexchange.com/questions/527396/display-number-in-tcolorbox-like-the-auto-number-in-equation
\newtcolorbox[auto counter, number within=section]{keypoints}[2][]{
    colback     =   blueEC!10,
    colframe    =   blueEC!80,
    arc         =   0pt,
    boxrule     =   0.5pt,
    fonttitle   =   \bfseries,
    title       = Box~\thetcbcounter: #2, #1,
}

% Custom table textbox
% https://tex.stackexchange.com/questions/527396/display-number-in-tcolorbox-like-the-auto-number-in-equation
\newtcolorbox[]{tablebox}[2][]{
    colback     =   blueEC!10,
    colframe    =   blueEC!80,
    arc         =   0pt,
    boxrule     =   0.5pt,
    fonttitle   =   \bfseries,
    title       = ,
}

% Notice and Title page 
% ~~~~~~~~~~~~~~~~~~~~
\makeatletter
\renewcommand{\maketitle}{%
    \begin{titlepage}
        \textcolor{white}{.} % hack to make vfill work
        \vfill
        \small 

        This publication is a Technical Report by the Joint Research Centre (JRC), the European Commission's science and knowledge service. It aims to provide evidence-based scientific support to the European policymaking process. The scientific output expressed does not imply a policy position of the European Commission. Neither the European Commission nor any person acting on behalf of the Commission is responsible for the use that might be made of this publication. Users should contact the referenced source for information on the methodology and quality underlying the data used in this publication for which the source is neither Eurostat nor other Commission services. The designations employed and the presentation of material on the maps do not imply the expression of any opinion whatsoever on the part of the European Union concerning the legal status of any country, territory, city or area or its authorities or the delimitation of its frontiers or boundaries.  
        
        \textbf{Contact Information:}
        
        Corresponding author: Andrea Blasco\\
        Email: andrea.blasco@ec.europa.eu\\
        Address: European Commission, JRC, Directorate S, Unit S.1, Brussels, Belgium\\
        
        
        \textbf{EU Science Hub}\\
        joint-research-centre.ec.europa.eu\\
        
        
        \textbf{JRC133518}\\
        Print: XXXXXX\\
        PDF: XXXXX\\
        
        \textbf{@ European Union, 2023}\\ 
        
        The reuse policy of the European Commission is implemented by Commission Decision 2011/833/EU of 12 December 2011 on the reuse of Commission documents (OJ L 330, 14.12.2011, p. 39). Unless otherwise noted, the reuse of this document is authorised under the Creative Commons Attribution 4.0 International (CC BY 4.0) licence (\url{https://creativecommons.org/ licenses/by/4.0}). This means that reuse is allowed, provided appropriate credit is given and any changes are indicated. For any use or reproduction of photos or other material the EU does not own, permission must be sought directly from the copyright holders.

        % Title page 
        \clearpage 
        \topskip=120pt
        \begin{center}
            \textbf{\color{blueEC}\Huge\@title}
            \vspace{60pt}
            {\Large\@date}
        \end{center}
    
        \vfill
        This publication was authored by \@author

    \end{titlepage}
}
\makeatother